Predictors of frog survival following translocations - create dataset

### 2022-03-12 code/translocation_survival_createdata.Rmd
Replace code to connect to database with scripts

## Create site characteristics dataset

### Connect to database

```{r db-connect1}
con = dbConnect(dbDriver("PostgreSQL"),
                host = Sys.getenv("host"), 
                port = Sys.getenv("port"), 
                dbname = Sys.getenv("dbname"),
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
               )
```

### Retrieve site-level data from database

@@

```{r db-disconnect1}
dbDisconnect(con)
rm(con)
```

### Add additional site characteristics

@@

### Save site characteristics dataset

```{r save-site-data}
translocation_sites %>% write_csv(here::here("data", "clean", "translocation_sites.csv"))
# translocation_sites <- read_csv(here::here("data", "clean", "translocation_sites.csv"))
```

### Combine translocation files from cmr-analysis repo

The files accessed by this code chunk are generated by code in the xxxxx_createdata_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo (version 2021).

```{r retrieve-translocated-frogs-data }
files <- fs::dir_ls("../data/raw/cmr-analysis/translocation")  
frog_translocation <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts numeric string from file path
  filter(release_date < "2021-01-01") %>% 
  rename(pit_tag_ref = pit_tag_id) %>% 
  select(-path)
rm(files)
```

```{r save-raw-translocated-frogs-data}
frog_translocation %>% write_csv(here::here("data", "raw", "frog_translocation_raw.csv"))
# frog_translocation <- read_csv(here::here("data", "raw", "frog_translocation_raw.csv"))
```

### Add frog characteristics from database

#### Connect to database

```{r db-connect2}
con = dbConnect(dbDriver("PostgreSQL"),
                host = Sys.getenv("host"), 
                port = Sys.getenv("port"), 
                dbname = Sys.getenv("dbname"),
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
               )
```

@@

#### Disconnect from database

```{r db-disconnect2}
dbDisconnect(con)
rm(con)
```

### Save raw frog characteristics dataset

```{r save-frog-characteristics-data}
frog_characteristics %>% write_csv(here::here("data", "raw", "frog_characteristics_raw.csv"))
# frog_characteristics <- read_csv(here::here("data", "raw", "frog_characteristics_raw.csv"))
```

@@

### Combine frog survival files from cmr-analysis repo

The files accessed by this code chunk are generated by code in the xxxxx_analysis_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo (version 2021).

```{r retrieve-frog-survival-data}
files <- fs::dir_ls("../data/raw/cmr-analysis/survival")
frog_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts numeric string from file path
  rename(years_since_intro = years_since_introduction,
         pit_tag_ref = pit_tag_id) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, pit_tag_ref, median_survival)
rm(files)
```

@@

```{r save-raw-frog-survival-data}
frog_survival %>% write_csv(here::here("data", "raw", "frog_survival_raw.csv"))
# frog_survival <- read_csv(here::here("data", "raw", "frog_survival_raw.csv"))
```

@@

```{r data-clean1}
frog_translocation <- frog_translocation %>% mutate(
  pit_tag_ref = replace(pit_tag_ref, site_id == "70641" & pit_tag_ref == "900067000117396", "900067000117397"))
frog_characteristics <- frog_characteristics %>% mutate(
  pit_tag_ref = replace(pit_tag_ref, release_siteid1 == 70641 & pit_tag_ref == "900067000117396", "900067000117397"))
frog_survival <-frog_survival %>% mutate(
  pit_tag_ref = replace(pit_tag_ref, site_id == "70641" & pit_tag_ref == "900067000117396", "900067000117397"))
```

@@

Check for null values and hat site_ids match expection

@@

```{r db-connect3}
#### Connect to database
con = dbConnect(dbDriver("PostgreSQL"),
                host = Sys.getenv("host"), 
                port = Sys.getenv("port"), 
                dbname = Sys.getenv("dbname"),
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
               )
```

```{r db-disconnect3}
dbDisconnect(con)
rm(con)
```
This code chunk indicates that there were likely no errors in sex recorded at recipient site when frogs were recaptured. 
Therefore, it is a useful check to compare sex recorded at translocation to sex recorded at recipient site. 
Three mismatches were detected. 
```{r check-sex}
frog_captures %>% distinct(pit_tag_ref, sex) %>% count(pit_tag_ref, sex) %>% filter(n > 1) # make sure that only one sex recorded per tag on recapture
frog_captures %>% distinct(pit_tag_ref, sex) %>% 
  rename(sexcapture = sex) %>% 
  inner_join(frog_translocation, by = "pit_tag_ref") %>% 
  filter(sex != sexcapture)
```

@@

Change sex at time of translocation based on subsequent recaptures at recipient site.

@@

```{r save_clean_translocation_data}
frog_translocation %>% 
   write_csv(here::here("data", "clean", "frog_translocation.csv"))
```

>>>>

## Create raw sites, frog characteristics, and frog captures data files

### Connect to database
```{r db-connect}
source("db_connect.R")
```

### Create site characteristics dataset

#### Retrieve site-level data from database

@@

#### Add additional site characteristics

@@

#### Save site characteristics dataset

```{r save-site-data}
translocation_sites %>% write_csv(here::here("data", "raw", "translocation_sites.csv"))
# translocation_sites <- read_csv(here::here("data", "raw", "translocation_sites.csv"))
```

### Create frog characteristics dataset

@@

#### Save raw frog characteristics dataset

```{r save-frog-characteristics-data}
frog_characteristics %>% write_csv(here::here("data", "raw", "frog_characteristics.csv"))
# frog_characteristics <- read_csv(here::here("data", "raw", "frog_characteristics.csv"))
```

### Create frog captures dataset for error checking step ("check-sex")

#### Retrieve frog captures from database

#### Save frog captures dataset

```{r save-frog-captures-data}
frog_captures %>% write_csv(here::here("data", "raw", "frog_captures.csv"))
# frog_captures <- read_csv(here::here("data", "raw", "frog_captures.csv"))
```

```{r db-disconnect}
source("db_disconnect.R")
```

### Combine translocation files

The files accessed by this code chunk are generated by code in the xxxxx_createdata_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo (version 2021), and copies are added to the /data/raw/cmr-analysis/translocation/ directory in this (i.e., translocation) repo.

```{r retrieve-translocated-frogs-data }
files <- fs::dir_ls("../data/raw/cmr-analysis/translocation")  
frog_translocation <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts site_id as numeric string from file path
  filter(release_date < "2021-01-01") %>%  # only include frogs translocated before 2021
  rename(pit_tag_ref = pit_tag_id) %>% 
  select(-path)
rm(files)
```

```{r save-raw-translocated-frogs-data}
frog_translocation %>% write_csv(here::here("data", "raw", "frog_translocation.csv"))
# frog_translocation <- read_csv(here::here("data", "raw", "frog_translocation.csv"))
```

@@

### Combine frog survival files

The files accessed by this code chunk are generated by code in the xxxxx_analysis_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo (version 2021), and copies are added to the /data/raw/cmr-analysis/survival/ directory in this (i.e., translocation) repo.

```{r retrieve-frog-survival-data}
files <- fs::dir_ls("../data/raw/cmr-analysis/survival")
frog_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts site_id as numeric string from file path
  rename(years_since_intro = years_since_introduction,
         pit_tag_ref = pit_tag_id) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, pit_tag_ref, median_survival)
rm(files)
```

@@

```{r save-raw-frog-survival-data}
frog_survival %>% write_csv(here::here("data", "raw", "frog_survival.csv"))
# frog_survival <- read_csv(here::here("data", "raw", "frog_survival.csv"))
```

@@

```{r data-clean1}
frog_translocation <- frog_translocation %>% 
  mutate(pit_tag_ref = replace(pit_tag_ref, site_id == "70641" & pit_tag_ref == "900067000117396", "900067000117397"))
frog_characteristics <- frog_characteristics %>% 
  mutate(pit_tag_ref = replace(pit_tag_ref, release_siteid1 == 70641 & pit_tag_ref == "900067000117396", "900067000117397"))
frog_survival <-frog_survival %>% 
  mutate(pit_tag_ref = replace(pit_tag_ref, site_id == "70641" & pit_tag_ref == "900067000117396", "900067000117397"))
```

@@

Check for null values and that donor-recipient site_ids match expectation

@@

The result from the first line of this code chunk indicates that there were likely no errors in sex recorded at recipient site when frogs were recaptured. 
Therefore, it is a useful check to compare sex recorded at translocation to sex recorded at recipient site (next 4 lines). 
Three mismatches were detected.

```{r check-sex}
frog_captures %>% distinct(pit_tag_ref, sex) %>% count(pit_tag_ref, sex) %>% filter(n > 1) # make sure that only one sex recorded per tag at recipient site

frog_captures %>% distinct(pit_tag_ref, sex) %>% 
  rename(sexcapture = sex) %>% 
  inner_join(frog_translocation, by = "pit_tag_ref") %>% 
  filter(sex != sexcapture)
```

@@

Change sex recorded at donor site at time of translocation, based on subsequent recaptures at recipient site.

@@

```{r save_clean_translocation_data}
frog_translocation %>% write_csv(here::here("data", "clean", "frog_translocation_final.csv"))
# frog_translocation <- read_csv(here::here("data", "clean", "frog_translocation_final.csv"))
```
